Species richness and network structure jointly drive total biomass and its temporal stability in fish communities

### 2020-11-17 manuscript/bef_stability/manuscript.Rmd
Update appendix

---
title: Species richness and network structure jointly drive total biomass and its temporal stability in fish communities
author: Alain Danet, Maud Mouchet, Willem Bonnaffe, Elisa Thebault, Colin Fontaine
date: \today 
output:
  bookdown::pdf_document2:
    toc: false 
    fig_caption: true 
    keep_tex: true
fontsize: 12pt
header-includes:
   - \usepackage{setspace}
   - \doublespacing
   - \usepackage{lineno}
   - \linenumbers
geometry: margin=2cm
bibliography: references.bib
---

@@

- Author affiliation:
  - Alain Danet: Centre d’Ecologie et des Sciences de la Conservation, UMR 7204
    MNHN-CNRS-Sorbonne Université, Muséum national d’Histoire naturelle de
    Paris, 43 rue Buffon, 75005 Paris, France
  - Maud Mouchet: Centre d’Ecologie et des Sciences de la Conservation, UMR 7204
    MNHN-CNRS-Sorbonne Université, Muséum national d’Histoire naturelle de
    Paris, 43 rue Buffon, 75005 Paris, France
  - Willem Bonnaffe: Ecological and Evolutionary Dynamics Lab. Zoology Research
    and Administration Building, 11a Mansfield Rd, Oxford OX1 3SZ, United
    Kingdom.
  - Elisa Thebault: Sorbonne Université, CNRS, IRD, INRAE, Université Paris Est
    Créteil, Institute of Ecology and Environmental Sciences of Paris
    (iEES-Paris), Paris, France  
  - Colin Fontaine: Centre d’Ecologie et des Sciences de la Conservation, UMR 7204
    MNHN-CNRS-Sorbonne Université, Muséum national d’Histoire naturelle de
    Paris, 43 rue Buffon, 75005 Paris, France

@@

Both biodiversity-ecosystem functioning (BEF) and foodweb complexity-stability
relationships have received considerable attention during the last decades.
Still, the BEF relationship remains rarely investigated in the context of food
webs, especially in empirical studies explicitly considering foodweb structures.
Foodweb stability-complexity relationship has been mainly the focus of
theoretical studies with very empirical testing. To fill this gap, we link
species richness, foodweb structure and annual biomass and its temporal
stability using a standardized monitoring of fish communities in French streams
running from 1995 to 2018. We inferred trophic interactions thanks to recorded
body size and diet literature. We reveal that species richness and average
trophic level had a positive relationship with annual biomass of fish
communities while they had respectively a negative and positive effect on its
temporal stability. We also found that the effects of stream size and
temperature on annual biomass and stability are mediated by their effects on
diversity and foodweb structure. Overall, our study opens fruitful perspectives
on the link between species richness, network structure, biomass and its
stability.

@@

Species richness promotes higher biomass production in a variety of ecosystems
and taxons. Indeed species richness generally increases primary productivity and
total biomass in experimental plant communities [@tilman_productivity_1996;
@grace_integrative_2016; @hector_plant_1999; @tilman_biodiversity_2014;
@grace_integrative_2016], but also in briophyte communities
[@mulder_physical_2001], stream feeders, [@cardinale_species_2002] and aquatic
bacterial consumers [@pennekamp_biodiversity_2018]. Despite the diversity of
ecosystems and taxons studied, the relationship between diversity and ecosystem
functioning remains traditionally focused on single trophic levels, ignoring the
effects of foodweb structure. Theoretical models have recently moved from
single trophic [@tilman_plant_1997;
@loreau_biodiversity_2001] to multitrophic communities [@thebault_food-web_2003;
@poisot_dissimilarity_2012; @schneider_animal_2016; @wang_biodiversity_2018]. 
These models show that both resource use complementarity and selection effects,
the two main mechanisms previously highlighted in single-trophic studies, are
also important to understand diversity effects in foodwebs
[@thebault_food-web_2003; @poisot_dissimilarity_2012; @schneider_animal_2016].
However, they also reveal new mechanisms such as positive effects of 
the number of trophic levels, i.e. associated with higher trophic levels, on ecosystem
functioning [@wang_biodiversity_2018]. Theoretical studies also showed that food
web properties, such as interaction distribution and strength, affect the
distribution of biomass among adjacent trophic levels
[@thebault_relationship_2006; @schneider_animal_2016; @barbier_pyramids_2019].
Despite these theoretical evidences that structure affects biomass, we are
lacking empirical studies that assess jointly how foodweb structure and species
diversity affect total biomass and its production.

@@

Several theoretical studies considering single trophic level have
clarified which mechanisms generate this positive relationship between species
richness and temporal
stability [@loreau_species_2008; @thibaut_understanding_2013], (1) species
synchrony and (2) species variability. Species synchrony captures to what extent
the fluctuations of abundances or biomasses through time are correlated among
species. A low synchrony in species fluctuations, i.e. asynchrony, is
synonymous of compensatory dynamic, where the decrease in abundance of a species
is compensated by the increase of an other. Asynchrony is generally the main
mechanism which species richness has a stabilizing effect on temporal
stability [@tilman_biodiversity_2006; @olivier_urbanization_2020]. Asynchrony is
expected to raise with the variability of species responses to perturbations. Though most
often positive, the relationship between species diversity and asynchrony has
also been evidenced to be neutral or negative in natural settings
[@tilman_biodiversity_2006; @thibaut_understanding_2013;
@olivier_urbanization_2020; @valencia_synchrony_2020].

@@

```{r}
myload(qt_station, dir = mypath("data"))
matmet_cap <- paste0( 
  "Yearly temporal series of networks of two stations having respectively a low
  (A) and high (B) temporal stability of biomass. A and B stations have
  respectively biomass stability the closest to the first and third quartile of
  the distribution of the temporal stability of biomass in the dataset,
  respectively ",
  round(qt_station$bm_std_stab[1],2), " and ", round(qt_station$bm_std_stab[2],
    2),
  ". Point size are proportional to the biomass of the trophic species. (C)
  Observation sites (black dots) were located across France and monitored on the
  period 1995-2018. Red dots being the location of (A) and (B) sites. ",
  "Inner borders draw the limits of the hydrographic basins. ", "(D) The metaweb
  of the study. Each trophic species (N = 412) is represented by a node and each
  color represent a species (S = 45). Resource nodes (7) were drawn in grey. ",
  "The species names corresponding to the three digit codes are found in Table
  SXX.")

@@

```{r matmet, fig.cap = matmet_cap, results = "fig.show", out.height="80%"}
library(knitr)
include_graphics(path = mypath("manuscript", "bef_stability", "figs", "fig1.pdf"),)
```

@@

The stations where the stream was of intermediate size could be sampled
alternatively with one of the two sampling protocols. In this case, we
kept only the most frequently used sampling protocol. Then, we selected the
stations that had been sampled ten years or more. There was low heterogeneity of
the sampling month within stations, with the median sampled month being
mid-August while the median of the standard deviation of the sampled month
within station was $0.7$. As the concept of community variability referred to
variability around an equilibrium, which is rarely observed or difficult to
characterize in natural communities, only stations with no temporal trends
in total biomass were selected (detailed in supplementary methods). However, the
results were robust to the relaxation of this hypothesis (Supplementary
results). These selection steps resulted in 99 stations distributed over seven
hydrographic basins (Figure \@ref(fig:matmet) A).

@@

Trophic interaction network was inferred from body size and ontogenic diet shift
following previous studies [@gravel_inferring_2013; @brose_predator_2019;
@poisot_structure_2016]. The diet of stream fishes, as for many organisms, shifts
throughout an individual's life, and thereby with body size. For example, alvins
feed on plankton while adults may feed on algae and fishes, with bigger individuals
eating bigger
fishes. Each fish species was hence divided in nine body size classes, each
corresponding to a trophic species (Figure S2). Additionally to the fish trophic
species, we added seven resource nodes present in the ontogenic food diet database:
detritus, biofilm, phytoplankton, zooplankton, macrophages, phytobenthos and
zoobenthos (grey nodes in Figure \@ref(fig:matmet) B, C & D). The fish trophic
species and the resources constituted the 412 nodes of the metaweb, 45 fish
species divided into nine body size classes plus seven resource nodes. The inference
of trophic interactions was shown to be more accurate when considering body size
classes, i.e. trophic species, than species [@jennings_weak_2001].

@@

```{r}
sem_caption <- paste0(
  "Metamodel of the Structural Equation Models for the (A) median of annual
  total biomass (in grams by square meter) and (C) its temporal stability.",
  "Results of the Structural Equation Models for
  (B) the determinants of the median of annual total biomass and (D) its temporal stability. Red and green
  arrows represent respectively negative and positive path coefficients. The
  path coefficients are standardized. For convenience, only significant
  paths (i.e. $P < 0.05$) are shown. Rsq: Ajusted $R^2$; Avg:
  Average, CVsp: weighted temporal CV of the population; PCA1 and PCA2: respectively the first and
  second axis of the PCA."
)
```

@@

## Species richness and average trophic level are positively correlated to total biomass

@@

The total effect of PCA2, related to average annual temperature and inversely to
altitude, on temporal stability was of higher magnitude than the effects of
species richness and mean trophic level (Table
\@ref(tab:indir-sem)).
The PCA2 had a total negative effect on temporal stability, meaning that higher
temperature results in lower stability
($r_\delta = `r env_on_stab$total["log_RC2"]`$, Table \@ref(tab:indir-sem)). 
PCA2 had an indirect positive effect on temporal stability through a
direct positive effect on $\overline{CV_{sp}}$ ($r_\delta = 
`r env_on_cv_sp$direct["log_RC2"]`$, Table \@ref(tab:indir-sem)) but also a
negative one through species richness but a positive one through
mean trophic level
(resp. $r_\delta = `r env_on_stab$via_richness["log_RC2"]`$ and
$r_\delta = `r env_on_stab$via_tlvl["log_RC2"]`$, Table \@ref(tab:indir-sem)).
This was also true for the PCA1, related to stream size, but effects were weaker
than for PCA2.

@@

library(kableExtra)
mytable <- kable(full_table,
  format = "latex",
  booktabs = T,
  label = paste0("indir-sem"),
  caption = caption_sem
  ) %>%
#kable_paper() %>%
kable_styling(latex_options =c("scale_down")) %>%
add_header_above(c(" " = 3, "Indirect effects via" = 5)) %>%
column_spec(1:2, width = "3cm") %>%
collapse_rows(columns = 1, valign = "top")
#str_replace(mytable, "\\\\#(.*)", "\\\\label{tab:indir-sem}")
#str_view(mytable, "\\\\#(.*)")
write(mytable, file = mypath("manuscript", "bef_stability", "table.tex"))
```

@@

The first step to identify the mechanisms behind those contrasting patterns is to
look at the effects of species richness on synchrony and $\overline{CV_{sp}}$.
As most studies on experimental grasslands
[@isbell_biodiversity_2009; @roscher_identifying_2011] and natural communities
of birds, grasslands, bats and butterflies [@bluthgen_land_2016;
@olivier_urbanization_2020], we found that species richness decreases synchrony,
thereby increasing stability [but see @declerck_species_2006;
@valencia_synchrony_2020]. Our study thus extends the evidence that species
richness decreases synchrony to the case of trophic communities in natural
settings. Species richness can reduce synchrony when (i) a given increase in species
richness leads to a decrease of population sizes which raises the role of
demographic stochasticity, when (ii) species have different
responses to environmental variation [@loreau_species_2008].

@@

Our study extends the assessment of the effect of species richness on total
annual biomass and its temporal stability in natural settings to the case of
foodwebs, while including network structure. Species richness had a direct
positive and negative effect respectively on total biomass and its stability but
mean trophic level had a positive effect on both. Furthermore, we found that
species richness had antagonistic effects on total biomass, through its effect
on mean trophic level. Our study thus highlights the importance of considering both
species richness, network structure and their dependence, though the
mechanisms remain to be elucidated. Finally, we found that
environmental gradient related to temperature and ecosystem size have
antagonistic effects on biomass and its temporal stability, positive through mean
trophic level and negative through species richness. Further research is needed
to find the mechanisms behind those pathways, that are crucial in context of
global changes.

One limitation of our study is that the use of inferred networks, i.e. not
observed interactions, and the lack of information about the foodwebs outside
fishes. But this approach is a promising way to explore how the architecture of
ecological networks vary along environmental gradients across time. It
constitutes an interesting complement to the real assessment of ecological
interactions. The use of inferred networks also allow to maximise the
information contained from already available long term datasets.

We look forward to see our findings and their interpretation tested by future
experimental and theoretical studies, allowing to unravel the ecological
mechanisms driving the complex relationships among environment, the structure of
ecological networks and ecosystem properties such as productivity and temporal
stability.

>>>>

---
title: Species richness and network structure jointly drive total biomass and its temporal stability in fish communities
author: Alain Danet, Maud Mouchet, Willem Bonnaffé, Elisa Thébault, Colin Fontaine
date: \today 
output:
  bookdown::pdf_document2:
    toc: false 
    fig_caption: true 
    keep_tex: true
fontsize: 12pt
header-includes:
   - \usepackage{setspace}
   - \doublespacing
   - \usepackage{lineno}
   - \linenumbers
geometry: margin=2cm
bibliography: references.bib
---

@@

- Author affiliation:
  - Alain Danet: Centre d’Ecologie et des Sciences de la Conservation, UMR 7204
    MNHN-CNRS-Sorbonne Université, Muséum national d’Histoire naturelle de
    Paris, 43 rue Buffon, 75005 Paris, France
  - Maud Mouchet: Centre d’Ecologie et des Sciences de la Conservation, UMR 7204
    MNHN-CNRS-Sorbonne Université, Muséum national d’Histoire naturelle de
    Paris, 43 rue Buffon, 75005 Paris, France
  - Willem Bonnaffé: Ecological and Evolutionary Dynamics Lab. Zoology Research
    and Administration Building, 11a Mansfield Rd, Oxford OX1 3SZ, United
    Kingdom.
  - Elisa Thébault: Sorbonne Université, CNRS, IRD, INRAE, Université Paris Est
    Créteil, Institute of Ecology and Environmental Sciences of Paris
    (iEES-Paris), Paris, France  
  - Colin Fontaine: Centre d’Ecologie et des Sciences de la Conservation, UMR 7204
    MNHN-CNRS-Sorbonne Université, Muséum national d’Histoire naturelle de
    Paris, 43 rue Buffon, 75005 Paris, France

@@

Both biodiversity-ecosystem functioning (BEF) and foodweb complexity-stability
relationships have received considerable attention during the last decades.
Still, the BEF relationship remains rarely investigated in the context of food
webs, especially in empirical studies explicitly considering foodweb structures.
Foodweb stability-complexity relationship has been mainly the focus of
theoretical studies with very little empirical testing. To fill this gap, we linked
species richness, foodweb structure, annual biomass and its temporal
stability using a standardized monitoring of fish communities in French streams
running from 1995 to 2018. We inferred trophic interactions from
body size recorded and diet literature. We reveal that species richness and average
trophic level had a positive relationship with annual biomass of fish
communities while they had respectively a negative and positive effect on its
temporal stability. We also found that the effects of stream size and
temperature on annual biomass and stability are mediated by their effects on
diversity and foodweb structure. Overall, our study opens fruitful perspectives
on the link among species richness, network structure, community biomass and its
temporal stability.

@@

Species richness promotes higher biomass production in a variety of ecosystems
and taxons. Indeed species richness generally increases primary productivity and
total biomass in experimental plant communities [@tilman_productivity_1996;
@grace_integrative_2016; @hector_plant_1999; @tilman_biodiversity_2014;
@grace_integrative_2016], but also in briophyte communities
[@mulder_physical_2001], stream feeders, [@cardinale_species_2002] and aquatic
bacterial consumers [@pennekamp_biodiversity_2018]. Despite the diversity of
ecosystems and taxons studied, the relationship between diversity and ecosystem
functioning remains traditionally focused on single trophic levels, ignoring the
effects of foodweb structure. Theoretical models have recently moved from
single trophic [@tilman_plant_1997;
@loreau_biodiversity_2001] to multitrophic communities [@thebault_food-web_2003;
@poisot_dissimilarity_2012; @schneider_animal_2016; @wang_biodiversity_2018]. 
These models show that both complementarity in the use of resources and selection effects,
the two main mechanisms previously highlighted in single-trophic studies, are
also important to understand diversity effects in foodwebs
[@thebault_food-web_2003; @poisot_dissimilarity_2012; @schneider_animal_2016].
However, they also reveal new mechanisms such as positive effects of 
the number of trophic levels, i.e. associated with higher trophic levels, on ecosystem
functioning [@wang_biodiversity_2018]. Theoretical studies also showed that food
web properties, such as interaction distribution and strength, affect the
distribution of biomass among adjacent trophic levels
[@thebault_relationship_2006; @schneider_animal_2016; @barbier_pyramids_2019].
Despite these theoretical evidence that structure affects biomass, we are
lacking empirical studies that assess jointly how foodweb structure and species
diversity affect total biomass and its production.

@@

Several theoretical studies considering a single trophic level have
clarified which mechanisms generate this positive relationship between species
richness and temporal
stability [@loreau_species_2008; @thibaut_understanding_2013], (1) species
synchrony and (2) species variability. Species synchrony captures to what extent
the fluctuations of abundances or biomasses through time are correlated among
species. A low synchrony in species fluctuations, i.e. asynchrony, is
synonymous of compensatory dynamic, where the decrease in abundance of a species
is compensated by the increase of an other. Asynchrony is generally the main
mechanism which species richness has a stabilizing effect on temporal
stability [@tilman_biodiversity_2006; @olivier_urbanization_2020]. Asynchrony is
expected to increase with the variability of species responses to perturbations. Though most
often positive, the relationship between species diversity and asynchrony has
also been evidenced to be neutral or negative in natural settings
[@tilman_biodiversity_2006; @thibaut_understanding_2013;
@olivier_urbanization_2020; @valencia_synchrony_2020].

@@

```{r}
myload(qt_station, dir = mypath("data"))
matmet_cap <- paste0( 
  "(A) Observation sites (black dots) were located across France and monitored
  on the period 1995-2018. The red dots show the location of (C) and (D) sites.
  ", " Inner borders draw the limits of the hydrographic basins. ", "(B) The
  metaweb of the study. Each trophic species (N = 412) is represented by a node
  and each
  color represent a species (S = 45). Resource nodes (7) were drawn in grey. ",
  "The species names corresponding to the three digit codes are found in Table
  SXX." ,
  "Yearly temporal series of networks of two stations having respectively a low
  (C) and high (D) temporal stability of biomass. C and D stations have
  respectively biomass stability the closest to the first and third quartile of
  the distribution of the temporal stability of biomass in the dataset,
  respectively ", round(qt_station$bm_std_stab[1],2), " and ",
  round(qt_station$bm_std_stab[2],
    2), ". Point size are proportional to the biomass of the trophic species.")

@@

```{r matmet, fig.cap = matmet_cap, results = "fig.show", out.height="80%"}
library(knitr)
include_graphics(path = mypath("manuscript", "bef_stability", "figs", "fig1.pdf"))
```

@@

The stations where the stream was of intermediate size could be sampled
alternatively with one of the two sampling protocols. In this case, we
kept only the most frequently used sampling protocol. Then, we selected the
stations that had been sampled ten years or more. There was low heterogeneity of
the sampling month within stations, with the median sampled month being
mid-August while the median of the standard deviation of the sampled month
within station was $0.7$. As the concept of community variability referred to
variability around an equilibrium, which is rarely observed or difficult to
characterize in natural communities, only stations with no temporal trends
in total biomass were selected (detailed in supplementary methods). However, the
results were robust to the relaxation of this hypothesis (Table SXX). These
selection steps resulted in 99 stations distributed over seven hydrographic
basins (Figure \@ref(fig:matmet) A).

@@

The trophic interaction network was inferred from body size and ontogenic diet shift
following previous studies [@gravel_inferring_2013; @brose_predator_2019;
@poisot_structure_2016]. The diet of stream fishes, as for many organisms, shifts
throughout an individual's life, and thereby with body size. For example, alvins
feed on plankton while adults may feed on algae and fishes, with bigger individuals
eating bigger
fishes. Each fish species was hence divided in nine body size classes, each
corresponding to a trophic species (Figure S2). Additionally to the fish trophic
species, we added seven resource nodes present in the ontogenic food diet database:
detritus, biofilm, phytoplankton, zooplankton, macrophages, phytobenthos and
zoobenthos (grey nodes in Figure \@ref(fig:matmet) B, C & D). The fish trophic
species and the resources constituted the 412 nodes of the metaweb, 45 fish
species divided into nine body size classes plus seven resource nodes. The inference
of trophic interactions was shown to be more accurate when considering body size
classes, i.e. trophic species, than species [@jennings_weak_2001].

@@

```{r}
sem_caption <- paste0(
  "Metamodel of the Structural Equation Models for the (A) median of annual
  total biomass (in grams by square meter) and (C) its temporal stability.",
  "Results of the Structural Equation Models for
  (B) the determinants of the median of annual total biomass and (D) its temporal stability. Red and green
  arrows represent respectively negative and positive path coefficients. The
  path coefficients are standardized. For convenience, only significant
  paths (i.e. $P < 0.05$) are shown. Rsq: Ajusted $R^2$; Avg:
  Average, CVsp: weighted temporal CV of the population; PCA1 and PCA2: respectively the first and
  second axis of the PCA performed on environmental variables (cf methods)."
)
```

@@

## Species richness and average trophic level are positively correlated with total biomass

@@

The total effect of PCA2, related to average annual temperature and inversely to
altitude, on temporal stability was of higher magnitude than the effects of
species richness and mean trophic level (Table
\@ref(tab:indir-sem)).
The PCA2 had a total negative effect on temporal stability, meaning that higher
temperature results in lower stability
($r_\delta = `r env_on_stab$total["log_RC2"]`$, Table \@ref(tab:indir-sem)). 
PCA2 had an indirect positive effect on temporal stability through a
direct positive effect on mean trophic level ($r_\delta = `r
env_on_stab$via_tlvl["log_RC2"]`$, Table \@ref(tab:indir-sem)). However, PCA2
had a negative effect on temporal stability through a direct positive effect on 
$\overline{CV_{sp}}$ and species richness (resp.  $r_\delta = 
`r env_on_cv_sp$direct["log_RC2"]`$ and $r_\delta = `r env_on_stab$via_richness["log_RC2"]`$,
Table \@ref(tab:indir-sem)). This was also true for the PCA1, related to stream
size, but effects were weaker than for PCA2.

@@

library(kableExtra)
mytable <- kable(full_table,
  format = "latex",
  booktabs = T,
  label = paste0("indir-sem"),
  caption = caption_sem
  ) %>%
kable_styling(latex_options =c("scale_down")) %>%
add_header_above(c(" " = 3, "Indirect effects via" = 5)) %>%
column_spec(1:2, width = "3cm") %>%
collapse_rows(columns = 1, valign = "top")
write(mytable, file = mypath("manuscript", "bef_stability", "table.tex"))
```

@@

The first step to identify the mechanisms behind those contrasting patterns is to
look at the effects of species richness on synchrony and $\overline{CV_{sp}}$.
As most studies on experimental grasslands
[@isbell_biodiversity_2009; @roscher_identifying_2011] and natural communities
of birds, grasslands, bats and butterflies [@bluthgen_land_2016;
@olivier_urbanization_2020], we found that species richness decreases synchrony,
thereby increasing stability [but see @declerck_species_2006;
@valencia_synchrony_2020]. Our study thus extends the evidence that species
richness decreases synchrony to the case of trophic communities in natural
settings. Species richness can reduce synchrony when (i) a given increase in species
richness leads to a decrease of population sizes which increases the impacts of
demographic stochasticity, when (ii) species have different
responses to environmental variation [@loreau_species_2008].

@@

Our study extends the assessment of the effect of species richness on total
annual biomass and its temporal stability in natural settings to the case of
foodwebs, while including network structure. Species richness had a direct
positive effect on total biomass and a negative effect on biomass stability.
Mean trophic level had a positive effect on both total biomass and its temporal
stability. Furthermore, we found that species richness had antagonistic effects
on total biomass, through its effect on mean trophic level. Our study thus
highlights the importance of considering both species richness, network
structure and their dependence, though the mechanisms remain to be elucidated.
Finally, we found that environmental gradient related to temperature and
ecosystem size have antagonistic effects on biomass and its temporal stability,
positive through mean trophic level and negative through species richness.
Further research is needed to find the mechanisms behind those pathways, and
crucial in the context of global change.

One limitation of our study is the use of inferred networks, i.e. not
observed interactions, and the lack of information about the foodwebs outside
fishes. But this approach is a promising way to explore how the architecture of
ecological networks vary along environmental gradients across time. It
constitutes an interesting complement to the real assessment of ecological
interactions. The use of inferred networks also allow to maximise the
information contained from already available long term datasets.

We look forward to seeing our findings and their interpretation tested by future
experimental and theoretical studies, allowing to unravel the ecological
mechanisms driving the complex relationships among environment, the structure of
ecological networks and ecosystem properties such as productivity and temporal
stability.
